---
title: "道路挖掘核定權責分工研究報告"
author: "Chiahua.Wang"
date: "2020/5/22"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r base,echo=F,message=F,warning=F}

library(dplyr)
library(jsonlite)
library(ggplot2)
library(knitr)

roadlist = read.csv(file("road_lev_length.csv",encoding = "big5"),stringsAsFactors = F)

if (file.exists("digcase1year.RData")) {
  load(file = "digcase1year.RData")
} else {
  alldig = fromJSON("http://roaddig.kinmen.gov.tw/KMDigAPI/api/OpenData/GetCaseList?sdate=2015-01-01&edate=2019-12-31")
alldig = alldig$Data

alldig = mutate(alldig,
                AllowStart=as.Date(AllowStart),
                AllowStop=as.Date(AllowStop),
                SchedStart=as.Date(SchedStart),
                SchedStop=as.Date(SchedStop),
                Length=as.numeric(Length),
                Width=as.numeric(Width),
                Area=as.numeric(Area))
alldig$Length[is.na(alldig$Length)] = round(mean(alldig$Length[!is.na(alldig$Length)]),0)
alldig$Width[is.na(alldig$Width)] = round(mean(alldig$Width[!is.na(alldig$Width)]),0)
alldig$Area[is.na(alldig$Area)] = round(mean(alldig$Area[!is.na(alldig$Area)]),0)

alldig = filter(alldig,!grepl("^\\(T",EngUse))

alldig =  filter(alldig,CaseStatus %in% c("一般進行狀態","已報完工待收件","已完工收件","已完工","完工回報退件"))

alldig$applydays = as.numeric(difftime(alldig$SchedStop,alldig$SchedStart,units="days"))
alldig = filter(alldig,!is.na(AllowStart))

alldig$lev = "道路"
for (i in 1:nrow(alldig)) {
  for (d in 1:nrow(roadlist)) {
    if (grepl(roadlist$roadname[d],alldig$Road[i])) {
      alldig$lev[i] = roadlist$lev[d]
      break
    } 
  }
}

save(alldig,file="digcase1year.RData")
}



```

## 目的

為改善道路挖掘決行層級的劃分決標，在最佳負荷與有效管理的條件下提升整體行政效率，爰以104至108年5年份之道路挖掘許可案紀錄，進行量化分析及研究。

近5年道挖基本資料如下：

+ 道路挖掘許可案量：平均每年`r round(nrow(alldig)/5,2)" 件
+ 申請挖掘長度：
  + 總長：平均每年`r round(sum(alldig$Length)/5,2)` 公尺
  + 25%位數：`r as.numeric(quantile(alldig$Length,0.25))` 公尺
  + 中位數：`r as.numeric(quantile(alldig$Length,0.50))` 公尺
  + 75%位數：`r as.numeric(quantile(alldig$Length,0.75))` 公尺
  + 平均： `r mean(alldig$Length)` 公尺
  + 標準差： `r sd(alldig$Length)` 公尺
+ 申請挖掘日數：
  + 25%位數：`r as.numeric(quantile(alldig$applydays,0.25))` 天
  + 中位數：`r as.numeric(quantile(alldig$applydays,0.5))` 天
  + 75%位數：`r as.numeric(quantile(alldig$applydays,0.75))` 天
+ 道路分級：
  + 涉及主要道路件數：`r nrow(alldig[alldig$lev=="主要道路",])` 件
  + 涉及次要道路件數：`r nrow(alldig[alldig$lev=="次要道路",])` 件
  + 其他：`r nrow(alldig[alldig$lev=="道路",])` 件

## 劃分方式

決策層級劃分，主要目的是減量分工，因此使用什麼條件、如何設定門檻為執行重點。為了讓分工能夠以量化指標快速劃分，在此提出三個衡量指標：

1. 涉及道路種類。例如依主要道路、次要道路等劃分，可連結對道路的重要性。
2. 挖掘長度。可連結對道路破壞的程度。
3. 申請施工日數。可連結對交通影響的程度。

```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("roadlev", label = "道路等級:",
              choices = c("主次要道路","主要道路","次要道路","所有道路"), selected = "主要道路"),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



